Pseudo-Relevance Query Performance Prediction for Information Retrieval

### 2017-03-01 qpp/paper.tex
final edits, submitting qpp

\maketitle
\begin{abstract}
\end{abstract}

@@

Query performance prediction (QPP) is the task of estimating the success of an information retrieval (IR) system in retrieving results for a submitted query. Prediction strategies generally use properties of the query or of the retrieved document set to quantify the success of a system. The former is called pre-retrieval prediction, while the latter is called post-retrieval prediction. On the whole, post-retrieval prediction outperforms pre-retrieval prediction, and our predictor belongs to this class.

@@

In this work, we propose a predictor inspired by pseudo-relevance feedback techniques that directly incorporates relevance metrics in the prediction process. We accomplish this by asserting that the top $r$ retreived documents in a ranked list for a query $Q$ are relevant to that query; we then use these pseudo-relevance judgments to estimate document retrieval evaluation using natural variations on the query: the top $n$ ranked documents.

@@

\begin{flalign}\label{eq.clarity}
\sum_{w \in V} P(w|Q) \log \frac{P(w|Q)}{P(w|C)}
\end{flalign}

@@

Zhou \& Croft's query feedback (QF) technique constructs a new query from the top ranked documents \cite{Zhou2007}. First, QF issues $Q$ against collection $C$, retrieving a results list $L$. By ranking each term $w$ in $L$ according to its contribution to query clarity (that is, its contribution to the KL-divergence with the collection) and selecting the top ranked terms, a new query $Q'$ is constructed. After retrieving results list $L'$ for $Q'$, the percentage overlap between $L$ and $L'$ is computed. This overlap is the QF score. This technique bears a resemblance to our proposed method: like ours, the top ranked results give rise to alternate queries, and the results lists of the original and alternate queries are compared. Unlike ours, however, QF produces only a single alternate query; our method also differs in its scoring component, which directly models retrieval performance rather than simply measuring overlap as QF does. Because of its similarity to our method, we use query feedback as a second baseline.

@@

In this paper, we employ the standard multinomial query likelihood (QL) retrieval model to rank the relevance of a document $D$ to query $Q$, although it should be noted that this model is not required by our query performance predictor.

Assuming a uniform distribution over documents, QL scores $D$ by the following:

@@

Our query performance predictor, which we call the pseudo-relevance performance predictor (PRPP), is inspired by the pseudo-relevance feedback technique of treating the top ranked documents as relevant to the query. Doing so allows us to directly model the robustness of query performance metrics to query perturbation. The broad steps of our approach are as follows:

\begin{enumerate}
	\item Issue query $Q$ against collection $C_p$; call the results list $R_p$
	\item Record the top $r$ documents in $R_p$ as relevant using each's normalized retrieval score as the degree of relevance
	\item Issue $Q$ against target collection $C_t$, if $C_p \neq C_t$; call the results list $R_t$
	\item For each document $D$ in $R_t$,
	\begin{enumerate}
		\item Construct a pseudo-query $Q_D$ consisting of the top $q$ non-stop terms\footnote{We remove terms in the standard Indri stoplist: http://www.lemurproject.org/stopwords/stoplist.dft} in $D$
		\item Issue $Q_D$ against $C_p$; call the results list $R_{pD}$
		\item Score $R_{pD}$ using the pseudo-relevance judgments from Step 2.
	\end{enumerate}
	\item Average the scores to compute a single score for $Q$
\end{enumerate}

\noindent Several points in the preceding would benefit from clarification.

First, our model makes no assertions about the identity of the performance collection $C_p$. While it is valid to use the target collection as the performance collection, we hypothesize that the use of an external collection may yield better results. We investigate this idea in Section \ref{section.results.external}.

Next, both $r$ and $q$ are free parameters in our approach. In fact, there are two other parameters in our approach: $k$ controls the length of $R_t$, while $n$ controls the length of $R_{pD}$. In general, all parameters should be set empirically. Although not required mathematically, we only allow values of $n$ where $n \leq r$ since setting $n$ greater than $r$ prevents us from retrieving all relevant documents.

One advantage to our model is the ability to predict specific retrieval metrics by estimating levels of relevance. Because these levels are normalized log probabilities, they consist of continuous values (in contrast to TREC qrels which contain binary or discrete relevance grades), but are still valid for metrics that incorporate graded relevance judgments like normalized discounted cumulative gain (nDCG). Metrics that use only binary relevance metrics, like mean average precision (MAP) follow the typical procedure of treating all judgments greater than zero as relevant.

@@

We also make use of Wikipedia\footnote{http://en.wikipedia.org} as an external collection in some experiments.

@@

Our predictor requires the setting of several parameters. We set $r$, $k$, and $n$ by cross-validation: we sweep over each parameter at the values $\{1, 5, 10, 20, 50, 75, 100\}$; as noted in Section \ref{section.method}, $n$ is only swept at values $\leq r$. We fix $q = 20$ for all runs since using the entire length of $D$, $|D|$, is excessively expensive during retrieval.

For each run, we split the query set into two equal sized folds and run 2-fold cross-validation, using the train fold to determine the optimal parameter settings to apply to the test fold. We choose an equal split over other forms of cross-validation in order to provide a relatively large number of queries to each fold, leading to more stable correlation values. We repeat this procedure 100 times, splitting the query set randomly each time, and average the correlation values to compute an average query performance prediction.

@@

% \begin{table}
% \begin{tabular}{|l|l|c|c|c|c|} \hline
% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
% Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
% \multirow{4}{*}{AP} & QC & \textbf{0.5280} & \textbf{0.6148} & 0.3564 & 0.4284 \\ \cline{2-6}
% & QF & 0.4240 & 0.5637 & 0.3202 & 0.4467 \\ \cline{2-6}
% & PRPP-flip & 0.5020 & 0.5661 & \textbf{0.4026} & \textbf{0.5092} \\ \cline{2-6}
% & PRPP & 0.5030 & 0.6115 & 0.4025 & 0.4880 \\ \hline\hline
% \multirow{4}{*}{wt10g} & QC & 0.2232 & 0.3636 & 0.0943 & 0.3436 \\ \cline{2-6}
% & QF & 0.1624 & 0.3847 & 0.0881 & 0.3613 \\ \cline{2-6}
% & PRPP-flip & 0.2910 & 0.4665 & 0.2367 & 0.3949 \\ \cline{2-6}
% & PRPP & \textbf{0.2850} & \textbf{0.4615} & \textbf{0.2529} & \textbf{0.4173} \\ \hline\hline
% \multirow{4}{*}{Robust} & QC & 0.4240 & 0.5114 & 0.3129 & 0.3914 \\ \cline{2-6}
% & QF & 0.2203 & 0.5073 & 0.1708 & 0.4926 \\ \cline{2-6}
% & PRPP-flip & 0.3826 & 0.5743 & 0.3540 & 0.5094 \\ \cline{2-6}
% & PRPP & \textbf{0.4381} & \textbf{0.5791} & \textbf{0.3222} & \textbf{0.5047} \\ \hline
% \end{tabular}
% \caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
% \label{table.results.self.pearson}
% \end{table}
% 
% \begin{table}
% \begin{tabular}{|l|l|c|c|c|c|} \hline
% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
% Corpus & Pred. & Med. & Max & Med. & Max \\ \hline\hline
% \multirow{4}{*}{AP} & QC & 0.3609 & 0.4440 & 0.2166 & 0.2807 \\ \cline{2-6}
% & QF & 0.3259 & 0.4215 & 0.2042 & 0.3100 \\ \cline{2-6}
% & PRPP-flip & 0.4068 & 0.4670 & \textbf{0.2769} & \textbf{0.3543} \\ \cline{2-6}
% & PRPP & \textbf{0.4132} & \textbf{0.4962} & 0.2701 & 0.3378 \\ \hline\hline
% \multirow{4}{*}{wt10g} & QC & 0.1561 & 0.3093 & 0.0712 & 0.2622 \\ \cline{2-6}
% & QF & 0.1599 & 0.2843 & 0.0657 & 0.2411 \\ \cline{2-6}
% & PRPP-flip & 0.2586 & 0.3772 & 0.2006 & 0.2844 \\ \cline{2-6}
% & PRPP & \textbf{0.2710} & \textbf{0.3642} & \textbf{0.1935} & \textbf{0.3053} \\ \hline\hline
% \multirow{4}{*}{Robust} & QC & 0.2985 & 0.3714 & 0.2266 & 0.2889 \\ \cline{2-6}
% & QF & 0.1895 & 0.3745 & 0.1389 & \textbf{0.3646} \\ \cline{2-6}
% & PRPP-flip & 0.3082 & 0.4148 & 0.2783 & 0.3698 \\ \cline{2-6}
% & PRPP & \textbf{0.3433} & \textbf{0.4273} & \textbf{0.2478} & 0.3634 \\ \hline
% \end{tabular}
% \caption{Median and maximum Kendall's $\tau$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
% \label{table.results.self.kendall}
% \end{table}

% \begin{table}
% \begin{tabular}{|l|l|c|c|c|c|} \hline
% & & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
% Corpus & Pred. & Valid. & Max. & Valid. & Max \\ \hline\hline
% \multirow{4}{*}{AP} & QC & 0.4748 & 0.6148 & 0.2488* & 0.4284 \\ \cline{2-6}
% & QF & 0.5178 & 0.5637 & 0.2368* & 0.4467 \\ \cline{2-6}
% & PRPP-flip & 0.4481 & 0.5661 & 0.4334 & 0.5092 \\ \cline{2-6}
% & PRPP & 0.5003 & 0.6115 & 0.3848 & 0.4880 \\ \hline\hline
% \multirow{4}{*}{wt10g} & QC & 0.2873 & 0.3636 & 0.2271* & 0.3436 \\ \cline{2-6}
% & QF & 0.3758 & 0.3847 & 0.3937 & 0.3613 \\ \cline{2-6}
% & PRPP-flip & 0.2758* & 0.4665 & 0.0957* & 0.3949 \\ \cline{2-6}
% & PRPP & 0.2533* & 0.4615 & -0.0181* & 0.4173 \\ \hline\hline
% \multirow{4}{*}{Robust} & QC & 0.4534 & 0.5114 & 0.3768 & 0.3914 \\ \cline{2-6}
% & QF & 0.5061 & 0.5073 & 0.4884 & 0.4926 \\ \cline{2-6}
% & PRPP-flip & 0.5581 & 0.5743 & 0.4889 & 0.5094 \\ \cline{2-6}
% & PRPP & 0.5602 & 0.5791 & 0.4986 & 0.5047 \\ \hline
% \end{tabular}
% \caption{Median and maximum Pearson's $r$ correlation of predictors for each collection. Bolded values are the largest observed per corpus/metric summary.}
% \label{table.results.self.pearson}
% \end{table}

\begin{table}
\begin{tabular}{|l|l|l|l|l|l|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Pred. & Valid. & Max. & Valid. & Max \\ \hline\hline
\multirow{3}{*}{AP} & QC & 0.3933 & 0.5742 & 0.1858 & 0.3487 \\ \cline{2-6}
& QF & 0.3561 & 0.5637 & 0.2386 & 0.4467 \\ \cline{2-6}
%& PRPP-flip & 0.3518 & 0.5661 & \textbf{0.2805} & \textbf{0.5092} \\ \cline{2-6}
& PRPP & \textbf{0.4152}$^{cf}$ & \textbf{0.6115} & \textbf{0.2513}$^{c}$ & \textbf{0.4880} \\ \hline\hline
\multirow{3}{*}{wt10g} & QC & 0.1054 & 0.2226 & 0.0027 & 0.0674* \\ \cline{2-6}
& QF & 0.2220 & 0.3847 & 0.1775 & 0.3613 \\ \cline{2-6}
%& PRPP-flip & 0.2687 & \textbf{0.4665} & 0.1961 & 0.3949 \\ \cline{2-6}
& PRPP & \textbf{0.2912}$^{cf}$ & \textbf{0.4615} & \textbf{0.1965}$^{c}$ & \textbf{0.4173} \\ \hline\hline
\multirow{3}{*}{Robust} & QC & 0.2942 & 0.4284 & 0.2292 & 0.3165 \\ \cline{2-6}
& QF & 0.3544 & 0.5073 & \textbf{0.3347} & 0.4926 \\ \cline{2-6}
%& PRPP-flip & 0.3973 & 0.5743 & \textbf{0.3410} & \textbf{0.5094} \\ \cline{2-6}
& PRPP & \textbf{0.3985}$^{cf}$ & \textbf{0.5791} & 0.3297$^{c}$ & \textbf{0.5047} \\ \hline
\end{tabular}
\caption{Cross-validated and maximum Pearson's $r$ correlation of predictors for each collection. $^c$ and $^f$ indicate statistically significant improvement at $p < 0.05$ over query clarity and query feedback respectively. Bolded values are the largest observed per corpus/metric summary. All correlations are statistically significant unless marked with an asterisk (*).}
\label{table.results.self.pearson}
\end{table}

\begin{table}
\begin{tabular}{|l|l|l|l|l|l|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
\multirow{3}{*}{AP} & QC & 0.3965 & 0.4157 & 0.1997 & 0.2276 \\ \cline{2-6}
& QF & 0.3601 & 0.4215 & 0.2381 & 0.3010 \\ \cline{2-6}
%& PRPP-flip & 0.4129 & 0.4670 & \textbf{0.2757} & \textbf{0.3543} \\ \cline{2-6}
& PRPP & \textbf{0.4554}$^{cf}$ & \textbf{0.4962} & \textbf{0.2521}$^{c}$ & \textbf{0.3378} \\ \hline\hline
\multirow{3}{*}{wt10g} & QC & 0.0779 & 0.1221* & -0.0017 & 0.0262*\\ \cline{2-6}
& QF & 0.2088 & 0.2843 & 0.1529 & 0.2411 \\ \cline{2-6}
%& PRPP-flip & \textbf{0.3020} & \textbf{0.3772} & 0.1960 & 0.2844\\ \cline{2-6}
& PRPP & \textbf{0.2734}$^{cf}$ & \textbf{0.3642} & \textbf{0.2207}$^{cf}$ & \textbf{0.3053} \\ \hline\hline
\multirow{3}{*}{Robust} & QC & 0.3070 & 0.3159 & 0.2357 & 0.2418 \\ \cline{2-6}
& QF & 0.3508 & 0.3745 & 0.3347 & \textbf{0.3646} \\ \cline{2-6}
%& PRPP-flip & 0.4029 & 0.4148 & 0.3410 & \textbf{0.3698} \\ \cline{2-6}
& PRPP & \textbf{0.4129}$^{cf}$ & \textbf{0.4273} & \textbf{0.3442}$^{cf}$ & 0.3634 \\ \hline
\end{tabular}
\caption{Cross-validated and maximum Kendall's $\tau$ correlation of predictors for each collection. $^c$ and $^f$ indicate statistically significant improvement at $p < 0.05$ over query clarity and query feedback respectively. Bolded values are the largest observed per corpus/metric summary. All correlations are statistically significant unless marked with an asterisk (*).}
\label{table.results.self.kendall}
\end{table}

@@

We report the average of the cross-validated runs in the "Valid." column. Values marked with superscripts indicate statistically significant improvement over baselines at $p < 0.05$ using a one-tailed paired t-test. The tables show that PRPP outperforms the baselines whenever MAP is the target metric; it also outperforms QC with nDCG@20 as the target metric in all cases and outperforms QF for wt10g and robust with Kendall's $\tau$ correlation.

We also report the maximum correlation value seen across all parameter settings. This is an oracle metric in that it uses the full set of queries and therefore the full set of relevance judgments. As can be seen in Tables \ref{table.results.self.pearson} and \ref{tbale.results.self.kendall}, the maximum prediction accuracy of PRPP is usually the highest across predictors and is often much higher than either baseline. The maximum value is included because it is suggestive of the potential of each predictor.

@@

\begin{table}
\begin{tabular}{|l|l|l|l|l|l|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
\multirow{2}{*}{AP} & QC-wiki & 0.1938$^{\downarrow}$ & & 0.0873$^{\downarrow}$ & \\ \cline{2-6}
& PRPP-wiki & 0.4495$^{\uparrow}$ & & 0.3593$^{\uparrow}$ & \\ \hline\hline
\multirow{2}{*}{wt10g} & QC-wiki & 0.1496$^{\uparrow}$ & & 0.0996$^{\uparrow}$ & \\ \cline{2-6}
& PRPP-wiki & 0.3344$^{\uparrow}$ & & 0.2851$^{\uparrow}$ & \\ \hline\hline
\multirow{2}{*}{Robust} & QC-wiki & 0.2359$^{\downarrow}$ & & 0.2078$^{\downarrow}$ & \\ \cline{2-6}
& PRPP-wiki & 0.3778$^{\downarrow}$ & & 0.2984$^{\downarrow}$ & \\ \hline
\end{tabular}
\caption{}
\label{table.results.wiki.pearson}
\end{table}

\begin{table}
\begin{tabular}{|l|l|l|l|l|l|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Pred. & Valid. & Max. & Valid. & Max. \\ \hline\hline
\multirow{2}{*}{AP} & QC-wiki & 0.1872$^{\downarrow}$ & & 0.0924$^{\downarrow}$ & \\ \cline{2-6}
& PRPP-wiki & 0.4693$^{\uparrow}$ & & 0.3589$^{\uparrow}$ & \\ \hline\hline
\multirow{2}{*}{wt10g} & QC-wiki & 0.1538$^{\uparrow}$ & & 0.1028$^{\uparrow}$ & \\ \cline{2-6}
& PRPP-wiki & 0.3272$^{\uparrow}$ & & 0.2845$^{\uparrow}$ & \\ \hline\hline
\multirow{2}{*}{Robust} & QC-wiki & 0.2295$^{\downarrow}$ & & 0.2001$^{\downarrow}$ & \\ \cline{2-6}
& PRPP-wiki & 0.3693$^{\downarrow}$ & & 0.3040$^{\downarrow}$ & \\ \hline
\end{tabular}
\caption{}
\label{table.results.wiki.kendall}
\end{table}

>>>>

\maketitle
\begin{abstract}
Techniques for estimating the effectiveness of an information retrieval system in the absence of relevance judgments, known as query performance prediction (QPP), generally work by associating some property of a query or its document result set with an evaluation metric like mean average precision. We propose a method of QPP that directly incorporates notions of relevance into the prediction process. To do this, we rely on the well-known information retrieval technique of pseudo-relevance feedback to approximate relevance judgments and to reformulate the query. Our experiments indicate that this approach is very effective at predicting query performance.
\end{abstract}

@@

Query performance prediction (QPP) is the task of estimating, without reference to relevance judgments, the success of an information retrieval (IR) system in retrieving results for a submitted query. Prediction strategies generally use properties of the query or of the retrieved document set to quantify the success of a system. The former is called pre-retrieval prediction, while the latter is called post-retrieval prediction. On the whole, post-retrieval prediction outperforms pre-retrieval prediction, and our predictor belongs to this class.

@@

In this work, we propose a predictor inspired by pseudo-relevance feedback techniques that directly incorporates relevance metrics in the prediction process. We accomplish this by asserting that the top retreived documents in a ranked list for a query are relevant to that query; we then use these pseudo-relevance judgments to estimate document retrieval evaluation using natural variations on the query derived from the top ranked documents.

@@

\begin{flalign}\label{eq.clarity}
clarity(Q) = \sum_{w \in V} P(w|Q) \log \frac{P(w|Q)}{P(w|C)}
\end{flalign}

@@

Zhou \& Croft's query feedback (QF) method is a query perturbation predictor that holds some resemblance to our own \cite{Zhou2007}. Their method begins by constructing a new query from the top ranked documents. First, QF issues $Q$ against collection $C$, retrieving a results list $L$. By ranking each term $w$ in $L$ according to its contribution to query clarity (that is, its contribution to the KL-divergence with the collection) and selecting the top ranked terms, a new query $Q'$ is constructed. After retrieving results list $L'$ for $Q'$, the percentage overlap between $L$ and $L'$ is computed. This overlap is the QF score. Like our proposed method, the top ranked results give rise to alternate queries, and the results lists of the original and alternate queries are compared. Unlike ours, however, QF produces only a single alternate query; our method also differs in its scoring component, which directly models retrieval performance rather than simply measuring overlap as QF does. Because of its similarity to our method, we use query feedback as a second baseline.

@@

Although our query performance predictor does not require it, in this paper we employ the standard multinomial query likelihood (QL) retrieval model to rank the relevance of a document $D$ to query $Q$.  Assuming a uniform distribution over documents, QL scores $D$ by the following:

@@

\begin{figure*}
%\centering
\includegraphics[width=\linewidth]{figures/example-queries.pdf}
\caption{Example pseudo-queries formed in our process. Each column displays the top five terms in the pseudo-query and their weights. The two original queries appear above ther respective pseudo-queries.}
\label{figure.queries}
\end{figure*}

Our query performance predictor, which we call the pseudo-evaluation performance predictor (PEval), is inspired by the pseudo-relevance feedback technique of treating the top ranked documents as relevant to the query. Doing so allows us to directly model the robustness of relevance metrics to query perturbation. We present the steps involved in our technique, followed by an explanation of key points:

\begin{enumerate}
	\item Issue query $Q$ against performance collection $C_p$; call the results list $R_p$
	\item Record the top $r$ documents in $R_p$ as relevant using each document's normalized retrieval score as the degree of relevance; all other documents are assumed to be non-relevant
	\item If $C_p \neq C_t$, issue $Q$ against target collection $C_t$; call the results list $R_t$
	\item For each document $D$ in $R_t$,
	\begin{enumerate}
		\item Construct a pseudo-query $Q_D$ consisting of the top $|Q_D|$ non-stop terms\footnote{We remove terms in the standard Indri stoplist: http://www.lemurproject.org/stopwords/stoplist.dft} in $D$
		\item Issue $Q_D$ against $C_p$; call the results list $R_{Q_D}$
		\item Score $R_{Q_D}$ for some relevance metric, e.g. average precision, using the pseudo-relevance judgments from Step 2.
	\end{enumerate}
	\item Average the scores computed in Step 4 to compute a single score for $Q$
\end{enumerate}

Essentially, our approach emulates an ad-hoc document retrieval evaluation using information from the true, original retrieval: we evaluate the ranked retrieval $R_{Q_D}$ for each query $Q_D$ using relevance judgments $R_p$.

Our model makes no assertions about the identity of the performance collection $C_p$. While it is valid to use the target collection as the performance collection, we hypothesize that the use of an external collection may yield better results. We investigate this idea in Section \ref{section.results.external}.

Both $r$ and $|Q_D|$ are free parameters in our approach, as are two additional parameters: $k$ controls the length of $R_t$, while $n$ controls the length of $R_{Q_D}$. In general, all parameters should be set empirically. Although not required mathematically, we only allow values of $n$ where $n \leq r$ since setting $n$ greater than $r$ prevents us from achieving perfect recall, i.e. from retrieving all pseudo-relevant documents.

One advantage to our model is the ability to predict specific retrieval metrics by estimating levels of relevance. As Step 2 states, we estimate levels of relevance by normalizing the retrieval scores of the documents in $R_p$. This follows from the pseudo-relevance feedback technique of treating top ranked documents as relevant by simply treating \textit{more highly} ranked documents as \textit{more relevant}. We use the normalized retrieval scores rather than the rankings themselves in order to allow documents to achieve similar levels of relevance if their scores are similar.

Because these relevance levels are normalized probabilities, they consist of continuous values (in contrast to TREC qrels which contain binary or discrete relevance grades), but are still valid for metrics that incorporate graded relevance judgments like normalized discounted cumulative gain (nDCG). Metrics that use only binary relevance metrics, like mean average precision (MAP), follow the typical procedure of treating all judgments greater than zero as relevant.

@@

We also make use of an indexed dump of Wikipedia\footnote{http://en.wikipedia.org} as an external collection in some experiments.

@@

Our predictor requires the setting of several parameters. We set $r$, $k$, and $n$ by cross-validation: we sweep over each parameter at the values $\{1, 5, 10, 20, 50, 75, 100\}$. As noted in Section \ref{section.method}, $n$ is only swept at values $\leq r$. We fix $|Q_D| = 20$ for all runs since using the entire length of $D$, $|D|$, is excessively expensive during retrieval.

For each run, we split the query set into two equal sized folds and run 2-fold cross-validation, using the train fold to determine the optimal parameter settings to apply to the test fold. We choose an equal split over other forms of cross-validation in order to provide a relatively large number of queries to each fold, leading to more stable correlation values. We repeat this procedure 100 times, splitting the query set randomly each time, and average the correlation values to compute an average query performance prediction score.

@@

\begin{table}[t]
\centering
\begin{tabular}{|l|l|l|l|l|l|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Run & Valid. & Max. & Valid. & Max \\ \hline\hline
\multirow{3}{*}{AP} & QC & 0.3933 & 0.5742 & 0.1858 & 0.3487 \\ \cline{2-6}
& QF & 0.3561 & 0.5637 & 0.2386 & 0.4467 \\ \cline{2-6}
%& PEval-flip & 0.3518 & 0.5661 & \textbf{0.2805} & \textbf{0.5092} \\ \cline{2-6}
& PEval & \textbf{0.4152}$^{cf}$ & \textbf{0.6115} & \textbf{0.2513}$^{c}$ & \textbf{0.4880} \\ \hline\hline
\multirow{3}{*}{wt10g} & QC & 0.1054 & 0.2226 & 0.0027 & 0.0674* \\ \cline{2-6}
& QF & 0.2220 & 0.3847 & 0.1775 & 0.3613 \\ \cline{2-6}
%& PEval-flip & 0.2687 & \textbf{0.4665} & 0.1961 & 0.3949 \\ \cline{2-6}
& PEval & \textbf{0.2912}$^{cf}$ & \textbf{0.4615} & \textbf{0.1965}$^{c}$ & \textbf{0.4173} \\ \hline\hline
\multirow{3}{*}{Robust} & QC & 0.2942 & 0.4284 & 0.2292 & 0.3165 \\ \cline{2-6}
& QF & 0.3544 & 0.5073 & \textbf{0.3347} & 0.4926 \\ \cline{2-6}
%& PEval-flip & 0.3973 & 0.5743 & \textbf{0.3410} & \textbf{0.5094} \\ \cline{2-6}
& PEval & \textbf{0.3985}$^{cf}$ & \textbf{0.5791} & 0.3297$^{c}$ & \textbf{0.5047} \\ \hline
\end{tabular}
\caption{Cross-validated and maximum Pearson's $r$ correlation of predictors for each collection. $^c$ and $^f$ indicate statistically significant improvement at $p < 0.05$ over query clarity and query feedback respectively. Bolded values are the largest observed per corpus/metric summary. All correlations are statistically significant unless marked with an asterisk (*).}
\label{table.results.self.pearson}
\end{table}

\begin{table}[t]
\centering
\begin{tabular}{|l|l|l|l|l|l|} \hline
& & \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{3-6}
Corpus & Run & Valid. & Max. & Valid. & Max. \\ \hline\hline
\multirow{3}{*}{AP} & QC & 0.3965 & 0.4157 & 0.1997 & 0.2276 \\ \cline{2-6}
& QF & 0.3601 & 0.4215 & 0.2381 & 0.3010 \\ \cline{2-6}
%& PEval-flip & 0.4129 & 0.4670 & \textbf{0.2757} & \textbf{0.3543} \\ \cline{2-6}
& PEval & \textbf{0.4554}$^{cf}$ & \textbf{0.4962} & \textbf{0.2521}$^{c}$ & \textbf{0.3378} \\ \hline\hline
\multirow{3}{*}{wt10g} & QC & 0.0779 & 0.1221* & -0.0017 & 0.0262*\\ \cline{2-6}
& QF & 0.2088 & 0.2843 & 0.1529 & 0.2411 \\ \cline{2-6}
%& PEval-flip & \textbf{0.3020} & \textbf{0.3772} & 0.1960 & 0.2844\\ \cline{2-6}
& PEval & \textbf{0.2734}$^{cf}$ & \textbf{0.3642} & \textbf{0.2207}$^{cf}$ & \textbf{0.3053} \\ \hline\hline
\multirow{3}{*}{Robust} & QC & 0.3070 & 0.3159 & 0.2357 & 0.2418 \\ \cline{2-6}
& QF & 0.3508 & 0.3745 & 0.3347 & \textbf{0.3646} \\ \cline{2-6}
%& PEval-flip & 0.4029 & 0.4148 & 0.3410 & \textbf{0.3698} \\ \cline{2-6}
& PEval & \textbf{0.4129}$^{cf}$ & \textbf{0.4273} & \textbf{0.3442}$^{cf}$ & 0.3634 \\ \hline
\end{tabular}
\caption{Cross-validated and maximum Kendall's $\tau$ correlation of predictors for each collection. $^c$ and $^f$ indicate statistically significant improvement at $p < 0.05$ over query clarity and query feedback respectively. Bolded values are the largest observed per corpus/metric summary. All correlations are statistically significant unless marked with an asterisk (*).}
\label{table.results.self.kendall}
\end{table}

A few sample pseudo-queries are shown in Figure \ref{figure.queries} along with the original query that they are meant to approximate. We can see that in general the pseudo-queries tend to stay related to the topic expressed in the original query; in some cases, however, such as the final pseudo-query shown for the original robust query, a great deal of noise can be introduced. This type of noise arises naturally from the language of the retrieved documents.

@@

We report the average of the cross-validated runs in the "Valid." column. Values marked with superscripts indicate statistically significant improvement over baselines at $p < 0.05$ using a one-tailed paired t-test. The tables show that PEval outperforms the baselines whenever MAP is the target metric; it also outperforms QC with nDCG@20 as the target metric in all cases and outperforms QF for wt10g and robust with Kendall's $\tau$ correlation.

We also report the maximum correlation value seen across all parameter settings. This is an oracle metric in that it uses the full set of queries and therefore the full set of relevance judgments. As can be seen in Tables \ref{table.results.self.pearson} and \ref{table.results.self.kendall}, the maximum prediction accuracy of PEval is usually the highest across predictors and is often much higher than either baseline. The maximum value is included because it is suggestive of the potential of each predictor.

@@

\begin{table}
\centering
\begin{tabular}{|l|l|l|l|l|l|} \hline
& \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{2-5}
Corpus & Valid. & Max. & Valid. & Max. \\ \hline\hline
% \multirow{2}{*}{AP} & QC$_w$ & 0.1938$^{\downarrow}$ & & 0.0873$^{\downarrow}$ & \\ \hline
AP & \textbf{0.4495}$^{\uparrow}$ & \textbf{0.6740} & \textbf{0.3593}$^{\uparrow}$ & \textbf{0.5742} \\ \hline
% \multirow{2}{*}{wt10g} & QC$_w$ & 0.1496$^{\uparrow}$ & & 0.0996$^{\uparrow}$ & \\ \hline
wt10g & \textbf{0.3344}$^{\uparrow}$ & \textbf{0.5487} & \textbf{0.2851}$^{\uparrow}$ & \textbf{0.5163} \\ \hline
% \multirow{2}{*}{Robust} & QC$_w$ & 0.2359$^{\downarrow}$ & & 0.2078$^{\downarrow}$ & \\ \hline
Robust & 0.3778$^{\downarrow}$ & 0.4821 & 0.2984$^{\downarrow}$ & 0.4333 \\ \hline
\end{tabular}
\caption{Pearson's $r$ correlation for PEval using Wikipedia as the performance collection. $\uparrow$ and $\downarrow$ indicate statistically significant ($p < 0.05$) improvement and decline, respectively, relative to the corresponding run in Table \ref{table.results.self.pearson}. Bolded values are greater than than the corresponding value in Table \ref{table.results.self.pearson}.}
\label{table.results.wiki.pearson}
\end{table}

\begin{table}
\centering
\begin{tabular}{|l|l|l|l|l|l|} \hline
& \multicolumn{2}{c|}{MAP} & \multicolumn{2}{c|}{nDCG@20} \\ \cline{2-5}
Corpus & Valid. & Max. & Valid. & Max. \\ \hline\hline
% \multirow{2}{*}{AP} & QC$_w$ & 0.1872$^{\downarrow}$ & & 0.0924$^{\downarrow}$ & \\ \hline
AP & \textbf{0.4693}$^{\uparrow}$ & \textbf{0.5082} & \textbf{0.3589}$^{\uparrow}$ & \textbf{0.4170} \\ \hline
% \multirow{2}{*}{wt10g} & QC$_w$ & 0.1538$^{\uparrow}$ & & 0.1028$^{\uparrow}$ & \\ \hline
wt10g & \textbf{0.3272}$^{\uparrow}$ & \textbf{0.4131} & \textbf{0.2845}$^{\uparrow}$ & \textbf{0.3781} \\ \hline
% \multirow{2}{*}{Robust} & QC$_w$ & 0.2295$^{\downarrow}$ & & 0.2001$^{\downarrow}$ & \\ \hline
Robust & 0.3693$^{\downarrow}$ & 0.3909 & 0.3040$^{\downarrow}$ & 0.3355 \\ \hline
\end{tabular}
\caption{Kendall's $\tau$ correlation for PEval using Wikipedia as the performance collection. $\uparrow$ and $\downarrow$ indicate statistically significant ($p < 0.05$) improvement and decline, respectively, relative to the corresponding run in Table \ref{table.results.self.kendall}. Bolded values are greater than than the corresponding value in Table \ref{table.results.self.kendall}.}
\label{table.results.wiki.kendall}
\end{table}

As mentioned in Section \ref{section.method.predicting}, PEval does not require that the performance collection and target collection be the same. One intuitive reason an external collection may be beneficial is if the top ranked documents $R_t$ are not representative of the true relevant documents in the collection; in this case, we would expect PEval to overpredict performance since the evaluation of the pseudo-queries based on $R_t$ is likely to mask the original query's failure to match dissimilar relevant documents. In contrast, if $R_p$ were derived from an external collection, we reduce the chance that the pseudo-relevant documents will exhibit the same bias that may affect $R_t$, thus improving our prediction.

%To understand the intuition behind using an external performance collection, consider an extreme case in which some form of collection bias causes the top ranked documents $R_t$ for query $Q$ in collection $C_t$ share \textit{no} vocabulary with the remainder of $C_t$. This does not imply that $R_t$ comprises the entirety of the relevant document set for $Q$---there may be relevant documents outside of $R_t$ that simply suffer from complete vocabulary mismatch---nor does it imply that all documents in $R_t$ are relevant. If we use $C_t$ as the performance collection $C_p$, we are likely to overestimate the query performance because the pseudo-relevant documents will consistently rank one another highly when issued as pseudo-queries.

%If, on the other hand, we use an external collection as $C_p$, we reduce the chance that the pseudo-relevant documents will exhibit the same vocabulary bias that may affect the top ranked documents in $C_t$, thus improving our estimation of the effects of query perturbation and improving our predictor's performance.
